---
title: 'Tarea 1: Cardex'
author: "Cocoletzi Conde Anayeli"
date: "29 de agosto de 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

# Primer Semestre
  
  *Programación Actuarial I                 05
  
  *Introducción a la Profeción Actuarial    08
  
  *DHPC                                     09
  
  *Conceptos de Cálculo                     05
  
  *Matematicas Basicas                      07
  
  *Problemas de Matematicas Basicas         07
  
     Promedio                                 7.75

# Segundo Semestre
  
  *Teoria del Interes I                     09
  
  *Microeconomia                            09
  
  *Formación Humana y Social                10
  
  *Geometria Analitica                      09
  
  *Conceptos de Cálculo                     08
  
  *Teoria de Ecuaciones                     07
  
    Promedio                                 8.66

# Tercer Semesre
  
  *Programación Actuarial II                08
  
  *Teoria del Interes II                    08
  
  *Algebra Lineal                           07
  
  *Macroeconomia                            07
  
  *Contabilidad General                     10
  
  *Cálculo Diferencial                      10
  
    Promedio                                 8.33

# Cuarto Semestre
  
  *Sistema Financiero Mexicano              10
  
  *Cálculo Integral                         10
  
  *DHTIC                                    10
  
  *Demografia                               07
  
  *Programación Actuarial II                07
  
  *Introducción a las Estructuras Algebraicas 05
  
    Promedio                                 8.33

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
